---
title: "Deliver and execute OHDSI studies"
author: "Marc A. Suchard and Martijn J. Schuemie"
date: "March 24, 2015"
output: beamer_presentation
---

## Goals

- Package code
    - Place code inside an `R` package extending `OHDSI/StudyProtocols/SkeletonStudy`
- Deliver to data-holding collaborators
    - Host package on `github`
- Execute analysis
    - Run in `R` and return results
- Collect results
    - Bad: email; better: hosted server

## Build a package

- "Derive" from `OHDSI/StudyProtocols/SkeletonStudy`
- Place code in `StudySpecifics.R` (example from `PGxDrugStudy`)
- Overload `execute()`

```{r eval=FALSE}
execute <- function(dbms, user, password, server, 
                    port = NULL,
                    cdmSchema, resultsSchema, 
    				file = getDefaultStudyFileName(),
                    ...) {    
    # Open DB connection
    # Create R objects as results
    # Close connection
    # Save objects
}
```

## Overload execute() function

```{r eval=FALSE}
    # Open DB connection
    connectionDetails <- 
        DatabaseConnector::createConnectionDetails(
            dbms=dbms, 
            server=server, 
            user=user, 
            password=password, 
            schema=cdmSchema, 
            port = port)    

    conn <- DatabaseConnector::connect(
        connectionDetails)
```

## Overload execute function

```{r eval=FALSE}
    # Count gender
    gender <- invokeSql("CountGender.sql", 
        dbms, conn, 
        "Executing gender count ...")    
    
    # Get frequencies
    frequencies <- invokeSql("GetFrequencies.sql", 
        dbms, conn, 
        "Executing frequency count ...")
```

## What does CountGender.sql look like?

```{r eval=FALSE}
SELECT CONCEPT.concept_name, 
    COUNT(DISTINCT(PERSON.person_id))
FROM DRUG_EXPOSURE,  PERSON, CONCEPT
WHERE DRUG_EXPOSURE.DRUG_EXPOSURE_START_DATE 
            >= DATE '2009-01-01'
AND   DRUG_EXPOSURE.DRUG_EXPOSURE_START_DATE 
            <= DATE '2012-12-31'
AND   DRUG_EXPOSURE.person_id = PERSON.person_id 
AND   PERSON.gender_concept_id = CONCEPT.concept_id
AND   (YEAR(DRUG_EXPOSURE.DRUG_EXPOSURE_START_DATE) 
            - PERSON.year_of_birth >= 0)
AND   (YEAR(DRUG_EXPOSURE.DRUG_EXPOSURE_START_DATE) 
            - PERSON.year_of_birth < 14)
GROUP BY CONCEPT.concept_name
ORDER BY CONCEPT.concept_name
```

## Overload execute function

```{r eval=FALSE}
    # List of R objects to save
    objectsToSave <- c("gender","frequencies")
    
    # Save results to disk
    saveOhdsiStudy(list = objectsToSave, file = file)
            
    # Clean up
    DBI::dbDisconnect(conn)    

    # Package and return result 
    # if return value is used	
    result <- mget(objectsToSave)
    class(result) <- "OhdsiStudy"
    invisible(result)
}
```

## Other functions to overload

```{r eval=FALSE}
# Package must provide a default gmail address 
# to receive result files
#' @keywords internal
getDestinationAddress <- function() { 
    return("nobody@gmail.com") }

# Package must provide a default result file name
#' @keywords internal
getDefaultStudyFileName <- function() { 
    return("OhdsiStudy.rda") }

# Packge must provide default email subject
#' @keywords internal
getDefaultStudyEmailSubject <- function() { 
    return("OHDSI Study Results") }
```

## Polishing the package

- Update documentation / example
    - Special arguments to `execute()`
    -  `roxygenise()`
- Update `DESCRIPTION`
    - Package name
- Run `R CMD check`
- Run `devtools::test(".")`
    - Need to specify
- Push to github
- Review?

## How to execute

- Data holding collaborators execute in ``R``

```{r eval=FALSE}
library(devtools)
install_github(c("OHDSI/SqlRender", 
                 "OHDSI/DatabaseConnector"))
install_github("OHDSI/StudyProtocols/PGxDrugStudy")
library(PGxDrugStudy)
execute(...)
email(from = "msuchard@ucla.edu",
      dataDescription = "I hold no real data")
```
