---
title: Appendix %number%
geometry: "left=1cm,right=1cm,top=1cm,bottom=2cm"
output: pdf_document
classoption: landscape
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage[table]{xcolor}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
---

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(ggplot2)
library(knitr) 
library(kableExtra) 
options(knitr.kable.NA = '')
tempFolder <- "S:/temp"
```

# Estimates for the comparison of %comparison% for the outcome of %outcome%

**Table**. Hazard ratios, 95% confidence intervals, nominal and empirically calibrated p-values using two time-at-risk follow-up strategies. DKA: diabetic ketoacidosis, event identified by diagnosis record in inpatient (IP)/emergency room (ER) claim (DKA IP/ER) or IP claim only (DKA IP), HR: Hazard Ratio, CI: Confidence Interval, p: Nominal p-value from conditional Cox proportional hazards model, Cal. P: Calibrated p-value based on the empirical p-value distribution of negative control outcomes. App.: The appendix where more supportive information about this analysis can be found, including population characteristics, propensity score distribution, study diagnostics and the Kaplan-Meier plot. Intent-to-Treat follow-up strategy: Analysis with all post-index observable time as time-at-risk where switching, augmentation, or discontinuation of the index drug is ignored. Per-Protocol: Analysis with on-treatment time-at-risk that ends at outcome event (DKA IP/ER or DKA IP), switching or augmentation, discontinuation of the index drug defined by the first refill gap of 90 days or greater, or end of observable time. Database-specific results are reported as NA where the outcome model did not converge. Meta-analysis results are reported as NA where between-study heterogeneity is I2 >= 40%.

```{r, echo = FALSE}
table <- readRDS(file.path(tempFolder, "temp.rds"))
kable(table, 
      row.names = FALSE, 
      format = "latex", 
      longtable = TRUE, 
      booktabs = TRUE, 
      linesep = c("", "", "", "", "", "\\addlinespace")) %>%
  kable_styling(font_size = 7, 
                latex_options = c("striped", "repeat_header"))
```
