---
title: Appendix %number%
geometry: "left=1cm,right=1cm,top=1cm,bottom=2cm"
output: pdf_document
classoption: landscape
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage[table]{xcolor}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
---

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(ggplot2)
library(knitr) 
library(kableExtra) 
options(knitr.kable.NA = '')
tempFolder <- "%tempFolder%"
```

# Estimates for the comparison of %comparison% for the outcome of %outcome%

**Table**. Hazard ratios, 95% confidence intervals, nominal and empirically calibrated p-values for various analyses. 

Remove Cana  
TRUE: patients in the comparator arm who were exposed to cana before or after the index therapy were excluded from the analysis  
FALSE: patients in the comparator arm who were exposed to cana before or after the index therapy were not excluded from the analysis, sensitivity analysis  
  
Metformin add on  
TRUE: Included only a subset of eligible patients who received metformin therapy prior to or on the date of the index therapy, sensitivity analysis  
FALSE: Included all eligible patients regardless of prior exposure to metformin therapy  

Time at risk  
On Treatment (30 day) (plus 30 day biological window after the last dose of the index therapy)  
On Treatment (0 day) (plus 0 day biological window after the last dose of the index therapy, sensitivity analysis)  
On Treatment (60 day) (plus 60 day biological window after the last dose of the index therapy, sensitivity analysis)  

Event type  
1st ever event (patients with a prior AP event was excluded from the analysis)  
1st post-index event (patients with a prior AP event was not excluded from the analysis)  

PS: Propensity Score  
HR: Hazard Ratio  
CI: Confidence Interval  
p: nominal p-value from conditional Cox proportional hazards model  
Cal. P: Empirically calibrated p-value based on the empirical p-value distribution of negative control outcomes     
ITT: Intent-To-Treat.   
App.: The appendix where more supportive information about this analysis can be found, including population characteristics, propensity score distribution, study diagnostics and the Kaplan-Meier plot.  

```{r, echo = FALSE}
table <- readRDS(file.path(tempFolder, "temp.rds"))
kable(table, 
      row.names = FALSE, 
      format = "latex", 
      longtable = TRUE, 
      booktabs = TRUE, 
      linesep = "") %>%
  kable_styling(font_size = 7, 
                latex_options = c("striped", "repeat_header"))
```

