---
title: "Study Results"
author: "Marc A. Suchard, MD, PhD"
date: "April 13, 2017"
output:
  pdf_document: 
    fig_caption: yes
  html_document: default
header-includes:
- \usepackage{pdflscape}
- \usepackage{rotating}
- \usepackage{multirow}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(xtable)
options(xtable.floating = FALSE)
options(xtable.timestamp = "")
options(xtable.comment = FALSE)
knitr::opts_chunk$set(fig.path = "figures/")

# Functions

getData <- function(folders) {
  do.call(rbind,
          lapply(folders, FUN = function(file) {
            table <- read.csv(file.path(studyFolder,
                                        file, "tablesAndFigures",
                                        "EmpiricalCalibration.csv"))
            table$db <- file
            table
          }))
}

getAttrition <- function(folders) {
  do.call(rbind,
          lapply(folders, FUN = function(file) {
            table <- read.csv(file.path(studyFolder,
                                        file, "Attrition.csv"))
            table$db <- file
            table
          }))
}

getStratifiedCounts <- function(strata, folders, isNumeric = TRUE) {
  zero <- data.frame(group = strata, countTreated = 0, countComparator = 0,
                     fractionTreated = 0, fractionComparator = 0)

  do.call(rbind, 
          lapply(folders, FUN = function(file) {
            table <- read.csv(file.path(studyFolder, 
                                        file, "tablesAndFigures", 
                                        "PopChar.csv"), as.is = TRUE)
            table <- table[table$group %in% strata,]
            start <- ifelse(isNumeric, 1, 2)
            table[,start:ncol(table)] <- sapply(table[,start:ncol(table)],
                                                as.numeric)
            table <- rbind(table, zero[!(zero$group %in% table$group), ])
            table <- table[order(table$group),]
            table$database <- file
            table
          }))
}

makeStratifiedPlot <- function(data, strata, databases, 
                               label1, label2,
                               strataLabel = strata,
                               ymax = 10000) {
  
  nstrata <- length(strata)
  
  # Make plot
  layout(matrix(1:(length(databases) + 2), ncol = 1))
  par(mar = c(1,4,1,6) + 0.1, xpd = NA)
  
  # Skip header plot
  plot(0,0, type = "n", axes = FALSE, ylab = "", xlab = "")
  
  # Body
  for (i in 1:length(databases)) {
    file <- databases[i]
    table <- data[data$database == file, ]
    
    barplot(as.matrix(data.frame(log(table$countTreated, 10),
                                 log(table$countComparator, 10))),
            axes = FALSE,
            axisnames = FALSE,
            ylim = c(0,log(ymax,10)), beside = TRUE)
    axis(2, at = c(0,1,2,3,4), 
         labels = c("0","10","100","1,000","10,000"), 
         las = 1)
    
    for (y in 0:4) {
      lines(c(0,3 + 2 * nstrata), rep(y, 2), lty = 2, lwd = 0.25)
    }
    
    lines(c(1,nstrata + 1), c(0,0))
    lines(c(nstrata + 2,2 * nstrata + 2), c(0,0))
    
    text(2 * nstrata + 5.5, 2, label1[i], srt = -90, cex = 1.5)
    text(2 * nstrata + 4,   2, label2[i], srt = -90, cex = 1.5)
    
    if (i == 1) {
      text(mean(1:nstrata)  + 1, 5.5, "Alendronate", cex = 1.5)
      text(mean((nstrata + 2):(2 * nstrata + 1)) + 1, 5.5, 
           "Raloxifene",  cex = 1.5)
    }
  }
  
  text(1:nstrata + 0.5, -0.5, strataLabel, srt = -90, adj = c(0,0.5))
  text((nstrata + 2):(2 * nstrata + 1) + 0.5, -0.5, 
       strataLabel, srt = -90, adj = c(0,0.5))
}

getOrder <- function(dbs, folders) {
  unlist(sapply(dbs, 
                function(x) { 
                  which(folders == x)
                }))
}

saveTable <- function(obj, number = NULL, filename) {
  first <- filename
  name <- paste(filename,".tex",sep="")
  sink(file=name)
  cat('
      \\documentclass[preview, 11pt]{standalone}
      \\usepackage{graphicx}
      \\usepackage[font = small]{caption}
      \\begin{document}
      ')
  if (!is.null(number)) cat(paste0("\\setcounter{table}{",number-1,"}"))
  cat("\\captionsetup{width=\\textwidth}")
  cat(obj)
  cat('
      \\end{document}
      ')
  sink()
  tools::texi2dvi(file=name)
  cmd <- paste("dvipng -T tight -D 600", shQuote(paste(first,".dvi",sep="")))
  invisible(system(cmd))
  cleaner <- c(".tex",".aux",".log",".dvi")
  invisible(file.remove(paste(first,cleaner,sep="")))
}

saveFigure <- function(filename, newFile, caption = NULL, number = NULL, width, height, newWidth = NULL) {
  if (is.null(newWidth)) newWidth = width
  first <- newFile
  name <- paste(newFile,".tex",sep="")
  sink(file=name)
  cat(paste0('
      \\documentclass[preview, 11pt]{standalone}
      \\usepackage{graphicx}
      \\usepackage[font = small]{caption}
      \\usepackage[textwidth=',newWidth,']{geometry}
      \\begin{document}
      '))
  if (!is.null(number)) cat(paste0("\\setcounter{figure}{",number-1,"}"))
  cat("\\begin{figure}[hbt]\\centering")
  cat("\\captionsetup{width=\\textwidth}")
  cat(paste0("\\includegraphics[width=\\textwidth,natwidth=",width,",natheight=",height,"]{",filename,"}"))
  if (!is.null(caption)) cat(paste0("\\caption{",caption,"}"))
  cat("\\end{figure}")
  cat('
      \\end{document}
      ')
  sink()
  tools::texi2dvi(file=name)
  cmd <- paste("dvipng -T tight -D 600", shQuote(paste(first,".dvi",sep="")))
  invisible(system(cmd))
  cleaner <- c(".tex",".aux",".log",".dvi")
  invisible(file.remove(paste(first,cleaner,sep="")))
}

```


```{r echo=FALSE}
studyFolder <- "/Users/msuchard/Dropbox/OHDSI/hip_fracture"
studyFolder <- "/Users/yuxitian/Dropbox/hip_fracture/"

folders <- c("PPlus", 
             "Optum_JRD", "CCAE_JRD", "CCAE_UNM",
             "MDCR_JRD", "MDCR_UNM", "MDCD_JRD", "Cerner", 
             "Columbia", "Stride", "NHIS")

label1 <- c("IMS", 
            "Optum", "Truven", "Truven",
            "Truven", "Truven", "Truven", "Cerner", 
            "Columbia", "Stanford")

label2 <-  c("PPlus", 
             "CEDM", expression(CCAE^1), expression(CCAE^2),
             expression(MDCR^1), expression(MDCR^2), "MDCD" ,"EHR" , 
             "EHR" , "Stride")

label3 <- c("IMS PPlus", 
            "Optum CEDM", 
            "Truven CCAE (1)", "Truven CCAE (2)",
            "Truven MDCR (1)", "Truven MDCR (2)", 
            "Truven MDCD", 
            "Cerner EHR", "Columbia EHR", "Stanford Stride")

folders = folders[c(1,2,3,5,7,8,9,10)]
label1 = label1[c(1,2,3,5,7,8,9,10)]
label2 = label2[c(1,2,3,5,7,8,9,10)]
label3 = label3[c(1,2,3,5,7,8,9,10)]
label2[3:4] = c("CCAE", "MDCR")
label3[3:4] = c("Truven CCAE", "Truven MDCR")
```


## Population characteristics

\clearpage

Year of study entry, stratified by drug exposure (alendronate / raloxifene) and data source.  Note patient counts are on the log-scale.

```{r echo=FALSE, fig.width=4.5, fig.height=9}
yearStrata <- c(2001:2012)
yearData <- getStratifiedCounts(yearStrata, folders)

makeStratifiedPlot(yearData, yearStrata, folders, label1, label2)

```

\clearpage

Age at study entry, stratified by drug exposure (alendronate / raloxifene) and data source.  Note patient counts are on the log-scale.

```{r echo=FALSE, fig.width=4.5, fig.height=9}
tmp <- seq(from = 45, to = 95, by = 5)
ageStrata <- paste0("Age group: ", tmp, "-", (tmp + 4))
ageData <- getStratifiedCounts(ageStrata, folders, isNumeric = FALSE)

makeStratifiedPlot(ageData, ageStrata, folders, label1, label2,
                   strataLabel = paste0(tmp, "-", (tmp + 4)))
```
<!--
```{r echo=FALSE, results = "asis"}
pop <- data.frame(group = 1, tn = 1, tp = 1, cn = 1, cp = 1)
for (file in folders) {
  table <- read.csv(file.path(studyFolder, file, "tablesAndFigures", "PopChar.csv"))
  table <- data.frame(group = table$group,
                      tn =  paste0(formatC(table$countTreated,
                                               format = "d",
                                               big.mark = ",")),
                      tp = paste0("(",
                                  formatC(round(table$fractionTreated * 100, 1), format = "f", digits = 1),")"),

                      cn = paste0(formatC(table$countComparator,
                                                  format = "d",
                                                  big.mark = ",")),
                      cp = paste0("(",
                                  formatC(round(table$fractionComparator * 100, 1), format = "f", digits = 1),
                                  ")")
                      )
  # table$treated <- as.character(table$treated)
  # table$comparator <- as.character(table$comparator)
  # table$treated[is.na(table$treated)] <- ""
  # table$comparator[is.na(table$comparator)] <- ""
  
  pop <- merge(pop, table, by = "group", all = TRUE)
  colnames(pop)[which(colnames(pop) == "tn.x")] <- "tn"
  colnames(pop)[which(colnames(pop) == "tp.x")] <- "tp"
  colnames(pop)[which(colnames(pop) == "cn.x")] <- "cn"
  colnames(pop)[which(colnames(pop) == "cp.x")] <- "cp"
  
  # pop$treated.y <- as.character(pop$treated.y)
  # pop$comparator.y <- as.character(pop$comparator.y)
  # pop$treated.y[is.na(pop$treated.y)] <- ""
  # pop$comparator.y[is.na(pop$comparator.y)] <- ""
  
  colnames(pop)[which(colnames(pop) == "tn.y")] <- paste0("tn_", file)
  colnames(pop)[which(colnames(pop) == "tp.y")] <- paste0("tp_", file)
  colnames(pop)[which(colnames(pop) == "cn.y")] <- paste0("cn_", file)
  colnames(pop)[which(colnames(pop) == "cp.y")] <- paste0("cp_", file)
}

pop <- pop[pop$group != "FEMALE",]
pop <- pop[pop$group != 1,]
pop <- pop[,colnames(pop) != "tn"]
pop <- pop[,colnames(pop) != "tp"]
pop <- pop[,colnames(pop) != "cn"]
pop <- pop[,colnames(pop) != "cp"]
pop[] <- lapply(pop, as.character)
pop[is.na(pop)] <- ""

colnames(pop) <- NULL
row.names(pop) <- NULL

# knitr::kable(pop[1:12,], row.names = FALSE, align = "c")
tab <- xtable(pop[1:12,])
align(tab) <- c("l","l",rep(c("r","l"),2 * length(folders)))
print(tab, include.rownames = FALSE, floating.environment = "sidewaystable")
```
-->

## Total patient and event counts (Intent-to-treat)


```{r echo=FALSE, results="asis"}
# allCohorts <- read.csv(system.file("settings", 
#                                    "CohortsToCreate.csv", 
#                                    package = "AlendronateVsRaloxifene"))
# allCohorts <- allCohorts[3:nrow(allCohorts),]


# invisible(mapply(allCohorts$cohortId, allCohorts$name, 
#                  FUN = function(outcomeId, name) {

printOutcomeTable <- function(analysisId,
                              folders, 
                              labels, 
                              cohortOrder, 
                              prettyCohortNames,
                              singleTable = FALSE,
                              caption = NULL,
                              floating = FALSE) {
  
  allCohorts <- read.csv(system.file("settings", 
                                     "CohortsToCreate.csv", 
                                     package = "AlendronateVsRaloxifene"))
  allCohorts <- allCohorts[3:nrow(allCohorts),]  
  
  allCohorts <- allCohorts[allCohorts$name %in% cohortOrder, ]

  allResults <- getData(folders)
  
  results <- allResults
  results <- results[results$analysisId == analysisId, ]
  results <- results[results$outcomeName %in% cohortOrder, ]
  results <- results[results$db %in% folders, ]
  
  results$space1 <- ""
  results$space2 <- ""
  
  results$treatedYears = round(results$treatedDays/365.24)
  results$comparatorYears = round(results$comparatorDays/365.24)
  
  results$order1 <- getOrder(results$db, folders)
  results$order2 <- getOrder(as.character(results$outcomeName), cohortOrder)
  results <- results[order(results$order2, 
                           results$order1,
                           decreasing = FALSE),]

  crude <- results[,c(# "space1",
                      "outcomeName",
                      "db","treated","treatedYears","eventsTreated",
                      "space2",
                      "comparator", "comparatorYears","eventsComparator",
                      "order1","order2")]
  temp = aggregate(crude[,c("treated","treatedYears","eventsTreated",
                            "comparator","comparatorYears","eventsComparator")],
                   by = list(outcomeName = crude$outcomeName),
                   sum)
  temp$db = "Total"
  temp$space2 = ""
  temp$order1 = rep(max(getOrder(results$db, folders))+1, nrow(temp))
  temp$order2 = getOrder(as.character(temp$outcomeName), cohortOrder)
  crude <- rbind(crude, temp)
  crude$outcomeName <- NULL
  crude <- crude[order(crude$order2,
                       crude$order1,
                       decreasing = FALSE),]
  crude$order1 <- NULL
  crude$order2 <- NULL
  
  crude$db <- c(labels, "Total") # paste0(label1, " ", label2)
  # crude$db <- sub("\\^(\\d)", "$^\\1$", crude$db)
  
  for (column in c("treated","comparator")) {
  crude[,column] <- formatC(crude[,column],
                            format = "d", big.mark = ",")
  }
  
  for (column in c("treatedYears", "comparatorYears")) {
    crude[,column] <- formatC(round(crude[,column] / 1), # / 1000?
                              format = "d", big.mark = ",")
  }
  
  for (column in c("eventsTreated", "eventsComparator")) {
    crude[,column] <- ifelse(crude[,column] < 6, 
                             ifelse(crude[,column] == 0, 0, "\\textless6"), 
                             formatC(crude[,column],
                                     format = "d", big.mark = ","))
  }
  
  # colnames(crude) <- c("Data source", 
  #                      "Patients", "Exposed days", "Events",
  #                      "Patients", "Exposed days", "Events" )
  addtorow = list()
  addtorow$pos <- c(list(0, 0, 0),
                    # as.list((length(folders)) * (0:(length(cohortOrder) - 1)) + 1),
                    nrow(crude)
                    # as.list(length(folders) * (0:(length(cohortOrder) - 1)))
  )
  if (singleTable) {
    addtorow$pos = c(addtorow$pos, nrow(crude) - 1)
  } else {
    addtorow$pos = c(addtorow$pos, as.list((length(folders)+1) * (0:(length(cohortOrder) - 1))))
  }
  
  getNameInBox <- function(name) {
    paste0("\\parbox[t]{2mm}{\\multirow{",
           round(length(folders) / 2),
           "}{*}{\\rotatebox[origin=c]{90}{",
           name,
           "}}}")    
  }
  
  getNameAcross <- function(name) {
    paste0("\\\\[-0.5em]\n \\multicolumn{8}{c}{",
           name,
           "} \\\\\n")
  }
  
  topStrut = "\\rule{0pt}{2.6ex}"
  botStrut = "\\rule[-1.2ex]{0pt}{0pt}"
  crude[(length(folders)+1)*(1:length(cohortOrder)),"db"] = paste0("\\multicolumn{1}{c}{",topStrut,botStrut,"Total}")
  
  #"\\multicolumn{1}{c}{\\rule{0pt}{2.6ex}\\rule[-1.2ex]{0pt}{0pt}Total}"
  
  addtorow$command <- c("& \\multicolumn{3}{c}{Alendronate} & & \\multicolumn{3}{c}{Raloxifene} \\\\\n",
                        "\\cline{2-4} \\cline{6-8} \\\\[-1em]\n",
                        "Data source & Patients & Years & Events & & Patients & Years & Events \\\\\n \\hline \n",
                        # getNameInBox(prettyCohortNames),
                        # rep("\\\\\n\\\\\n", length(cohortOrder))
                        "[0.4em]\\hline"
                        )
  if (singleTable) {
    addtorow$command = c(addtorow$command, "[0.5em]\\hline")
  } else {
    addtorow$command = c(addtorow$command, getNameAcross(prettyCohortNames))
  }
  
  tab <- xtable(crude, caption = caption)
  
  align(tab) <- "clrrrcrrr"
  print.xtable(tab, include.rownames = FALSE, include.colnames = FALSE,
               add.to.row = addtorow,
               hline.after = c(-1),
               sanitize.text.function=function(x) { x },
               floating = floating)
}

cohortOrder1 <- c("HipFracture", 
                  "VertebralFracture", 
                  "AtypicalFemuralFracture")

prettyCohortNames1 <- c("Hip fracture", 
                        "Vertebal fracture", 
                        "Atypical femural fracture")

printOutcomeTable(analysisId = 1, folders, paste0(label1, " ", label2), cohortOrder1, prettyCohortNames1)
```

```{r echo=FALSE, results="asis"}
cohortOrder2 <- c("EsophagealCancer",
                   "OsteonecrosisOfJaw")

prettyCohortNames2 <- c("Esophageal cancer", 
                        "Osteonecrosis of the jaw")

printOutcomeTable(analysisId = 1, folders, paste0(label1, " ", label2), cohortOrder2, prettyCohortNames2)
# }))
```

```{r echo=FALSE, results="asis"}
printOutcomeTable(analysisId = 1, folders, paste0(label1, " ", label2), "HipFracture", "", singleTable = TRUE, caption = "Number of patients, observation years, and number of hip fracture events in study cohort by database", floating = FALSE)
```

## Incidence Among All
```{r echo=FALSE, results="asis"}
printOverallIncidence <- function(analysisId,
                                  folders, 
                                  labels, 
                                  cohortOrder, 
                                  prettyCohortNames) {
  
  
  allCohorts <- read.csv(system.file("settings", 
                                     "CohortsToCreate.csv", 
                                     package = "AlendronateVsRaloxifene"))
  allCohorts <- allCohorts[3:nrow(allCohorts),]  
  
  allCohorts <- allCohorts[allCohorts$name %in% cohortOrder, ]

  allResults <- getData(folders)
  
  results <- allResults
  results <- results[results$analysisId == analysisId, ]
  results <- results[results$outcomeName %in% cohortOrder, ]
  results <- results[results$db %in% folders, ]
  
  results$space1 <- ""
  results$space2 <- ""
  
  results$order1 <- getOrder(results$db, folders)
  results$order2 <- getOrder(as.character(results$outcomeName), cohortOrder)
  results <- results[order(results$order2, 
                           results$order1,
                           decreasing = FALSE),]
  
  results$treatedYears = round(results$treatedDays/365.24)
  results$comparatorYears = round(results$comparatorDays/365.24)

  crude <- results[,c(# "space1",
                      "outcomeName",
                      "treated","treatedYears","eventsTreated",
                      "comparator","comparatorYears","eventsComparator")]
  
  crude <- aggregate(crude[,-c(1)], by = list(outcomeName = crude$outcomeName), sum)
  crude <- crude[match(cohortOrder,crude$outcomeName),]
  crude$outcomeName <- prettyCohortNames
  #crude$treatedIncidence = crude$eventsTreated/crude$treatedYears
  #crude$comparatorIncidence = crude$eventsComparator/crude$comparatorYears
  
  crude$treatedRate = crude$eventsTreated/crude$treatedYears*1000
  crude$comparatorRate = crude$eventsComparator/crude$comparatorYears*1000

  
  crude$space = ""

  crude = crude[,c("outcomeName","treated","treatedYears","eventsTreated","treatedRate","space",
                   "comparator","comparatorYears","eventsComparator","comparatorRate")]

  # for (column in c("treatedIncidence", "comparatorIncidence")) {
  #   crude[,column] <- paste0(formatC(100 * crude[,column], digits = 3), "\\%")
  # }
  
  for (column in c("eventsTreated", "eventsComparator", "treatedYears", "comparatorYears")) {
    crude[,column] <- ifelse(crude[,column] < 6,
                             ifelse(crude[,column] == 0, 0, "\\textless6"),
                             formatC(crude[,column],
                                     format = "d", big.mark = ","))
  }
  
  # for (row in 1:nrow(crude)) {
  #   if (crude$eventsTreated[row] == "<6") {
  #     crude$treatedIncidence[row] = paste0("<",formatC(100*6/crude$treated[row], digits = 3), "\\%")
  #   }
  #   if (crude$eventsComparator[row] == "<6") {
  #     crude$comparatorIncidence[row] = paste0("<",formatC(100*6/crude$comparator[row], digits = 3), "\\%")
  #   }
  # }
  
  for (column in c("treated","comparator")) {
    crude[,column] <- formatC(crude[,column],
                              format = "d", big.mark = ",")
  }
  

  addtorow <- list()
  addtorow$pos <- c(list(0,0,0),
                    nrow(crude))


  getNameInBox <- function(name) {
    paste0("\\parbox[t]{2mm}{\\multirow{",
           round(length(folders) / 2),
           "}{*}{\\rotatebox[origin=c]{90}{",
           name,
           "}}}")
  }

  getNameAcross <- function(name) {
    paste0("\\\\[-0.5em]\n \\multicolumn{8}{c}{",
           name,
           "} \\\\\n")
  }

  addtorow$command <- c("& \\multicolumn{4}{c}{Alendronate} & & \\multicolumn{4}{c}{Raloxifene} \\\\\n",
                        "\\cline{2-5} \\cline{7-10} \\\\[-1em]\n",
                        "\\multicolumn{1}{c}{Outcome} & Patients & Years & Events & Rate & & Patients & Years & Events & Rate \\\\\n                             \\hline \\\\ [-0.5em] \n",
                        "[0.5em] \\hline \\\\ [-0.5em] \\multicolumn{10}{l}{Rate: incidence per 1,000 person-years}")
  
  tab <- xtable(crude)
  
  align(tab) <- "clrrrrcrrrr"
  print.xtable(tab, include.rownames = FALSE, include.colnames = FALSE,
               add.to.row = addtorow,
               hline.after = c(-1),
               sanitize.text.function=function(x) { x }
               )
}
cohortOrder3 <- c("HipFracture", 
                  "VertebralFracture", 
                  "AtypicalFemuralFracture",
                  "EsophagealCancer",
                   "OsteonecrosisOfJaw")
prettyCohortNames3 <- c("Hip fracture", 
                        "Vertebal fracture", 
                        "Atypical femural fracture",
                        "Esophageal cancer", 
                        "Osteonecrosis of the jaw")

printOverallIncidence(analysisId = 1, folders, paste0(label1, " ", label2), cohortOrder3, prettyCohortNames3)
```


## Total patient and event counts (Per-protocol)


```{r echo=FALSE, results="asis"}
toRemove = match(c("PPlus","Cerner"),folders)
#notPPlus <- !(folders == "PPlus" | folders == "Cerner")

printOutcomeTable(analysisId = 2,
                  folders = folders[-toRemove], paste0(label1, " ", label2)[-toRemove],
                  cohortOrder1, prettyCohortNames1)
```

```{r echo=FALSE, results="asis"}
printOutcomeTable(analysisId = 2,
                  folders = folders[-toRemove], paste0(label1, " ", label2)[-toRemove],
                  cohortOrder2, prettyCohortNames2)

```

## Incidence Among All
```{r echo=FALSE, results="asis"}
printOverallIncidence(analysisId = 2, folders[-toRemove], paste0(label1, " ", label2)[-toRemove], cohortOrder3, prettyCohortNames3)
```


\clearpage

## Attrition from PS Trimming
```{r echo = FALSE, results = "asis"}
printAttrition <- function(folders,
                           labels,
                           caption = NULL,
                           floating = FALSE) {
  results <- getAttrition(folders)
  #results$space1 <- ""

  results$order1 <- getOrder(results$db, folders)
  results <- results[order(results$order1,
                           decreasing = FALSE),]
  results <- results[results$description%in%c("No prior outcome", "Trimmed to equipoise"),]
  results <- results[,c("description", "treatedPersons", "comparatorPersons")]
  results$totalPersons = results$treatedPersons + results$comparatorPersons
  
  results1 <- results[results$description == "No prior outcome", -c(1)] - 
    results[results$description == "Trimmed to equipoise", -c(1)]
  
  crude <- results1 / results[results$description == "No prior outcome", -c(1)]

  for (column in c("treatedPersons", "comparatorPersons", "totalPersons")) {
    crude[,column] <- paste0(formatC(100 * crude[,column], digits = 2), "\\%")
  }
  
  crude$db <- c(labels) # paste0(label1, " ", label2)
  crude$db <- sub("\\^(\\d)", "$^\\1$", crude$db)
  
  crude = crude[,c("db","treatedPersons","comparatorPersons","totalPersons")]
  
  addtorow <- list()
  addtorow$pos <- c(list(0), nrow(crude))

  addtorow$command <- c("\\multicolumn{1}{c}{Data source}& Alendronate & Raloxifene & Total \\\\ \\hline \\\\[-0.5em]\n",
                         "[0.4em]\\hline")

  tab <- xtable(crude, caption = caption)
  
  align(tab) <- "clrrr"
  print.xtable(tab, include.rownames = FALSE, include.colnames = FALSE,
               add.to.row = addtorow,
               hline.after = c(-1),
               sanitize.text.function=function(x) { x },
               floating = floating
  )
}
  
printAttrition(folders, paste0(label1, " ", label2))
  
```

\clearpage

## Covariate balance statistics

```{r, echo=FALSE, results="asis"}
printBalance <- function(folders,
                         caption = NULL,
                         floating = FALSE) {
  table <-
    do.call(rbind, 
            lapply(folders, FUN = function(file) {
              table <- read.csv(file.path(studyFolder, 
                                          file, 
                                          "Balance.csv"), as.is = TRUE)
              idx <- which(folders == file)
              name <- paste0(label1[idx], " ", label2[idx])
              name <-  sub("\\^(\\d)", "$^\\1$", name)
              table <- data.frame(db = name,
                                  before = max(abs(table$beforeMatchingStdDiff),
                                               na.rm = TRUE),
                                  after = max(abs(table$afterMatchingStdDiff),
                                              na.rm = TRUE))
              table
            }))
  
  addtorow <- list()
  addtorow$pos <- list()
  addtorow$pos[[1]] <- 0
  addtorow$pos[[2]] <- nrow(table)
  addtorow$command <- c("\\multicolumn{1}{c}{Data source} & \\multicolumn{1}{c}{Before PS} & \\multicolumn{1}{c}{After PS}  \\\\\n \\hline \\\\[-0.5em]",
                        "[0.4em]\\hline")  
  
  output <- xtable(table, caption = caption)
  
  align(output) <- "clrr"
  print.xtable(output, include.rownames = FALSE, include.colnames = FALSE,
               add.to.row = addtorow,
               hline.after = c(-1),
               sanitize.text.function=function(x) { x },
               floating = floating
  )
}
printBalance(folders)
```

## Residual bias using negative controls

```{r, echo=FALSE, warning=FALSE, fig.height=8}
library(grid)
library(gridExtra)
library(ggplot2)

multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL, byrow = FALSE) {
  library(grid)

  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)

  numPlots = length(plots)

  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                    ncol = cols, nrow = ceiling(numPlots/cols), byrow = byrow)
  }

 if (numPlots==1) {
    print(plots[[1]])

  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))

    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))

      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}

  pathToCsv <- system.file("settings", "NegativeControls.csv", package = "AlendronateVsRaloxifene")
  negativeControls <- read.csv(pathToCsv)
  negControlCohortIds <- negativeControls$conceptId

# layout(matrix(1:(2 * length(folders)), ncol = 2, byrow = TRUE))
#par(mar = c(1,1,1,1) + 0.1, xpd = NA)

# plot(0,0, type = "n",
#      xlim = c(0,2),
#      ylim = c(0,length(folders)))

# for (idx in 1:length(folders)) {
  pl <- lapply(1:length(folders), FUN = function(idx) {
  
  file <- folders[idx]
  # fig <- png::readPNG(file.path(studyFolder, 
  #                                       file, "tablesAndFigures",
  #                                       "CalEffectNoHoi_a1.png"))
  # rasterImage(fig, 0.1, 0.1, 1.9, 9.9)
  #plot(0,0)
  #plot(0,0)
  print(file)
  
   emp <-  read.csv(file.path(studyFolder, 
                                        file, "tablesAndFigures",
                                        "EmpiricalCalibration.csv"))

   emp <- emp[emp$analysisId == 1 & emp$outcomeId %in% negControlCohortIds, ]
  base <- EmpiricalCalibration::plotCalibrationEffect(emp$logRr, emp$seLogRr)
  text <- textGrob(label = paste0(label1[idx], " ", label2[idx]),
                    gp = gpar(cex = 1.25),
                    rot = 0)
  ann <- ggplot2::annotation_custom(
    grob = text,
    ymin = 1.4, ymax = 1.4,
    xmin = 0.4, xmax = log(2))
  # list(base,ggplot() + ann)
  base + ann
})
  multiplot(plotlist = pl, cols = 2)
  
#   pl[[1]] + ggplot2::annotation_custom(
#     grob = textGrob(label = paste0("HELLO"),
#                     gp = gpar(cex = 1.5),
#                     rot = -90),
#     ymin = 0.75, ymax = 0.75,
#     xmin = log(8), xmax = 0)
#   
# multiplot(
#   pl[[1]][[1]],
#  pl[[1]][[2]] + 
#    theme(panel.background = element_blank()) + 
#    coord_fixed(ratio = 0.5)  ,
#  cols = 2
# )
  
```

\clearpage

## Hip fracture effect estimate (intent-to-treat)

```{r, echo=FALSE, warning=FALSE, fig.height=4, fig.width=7}

plotForest <- function(logRr, logLb95Ci, logUb95Ci, names, labels,
                       xLabel = "Relative risk", 
                       breaks = c(0.25, 0.5, 1, 2, 4, 6, 8, 10),
                       summaryExclude = c(),
                       plotExclude = c(),
                       fileName = NULL) {
  
              # logRr = results$logRr
              # logLb95Ci = log(results$ci95lb)
              # logUb95Ci = log(results$ci95ub)
              # names = results$db
              # labels = label3
              # xLabel = "Hazard Ratio"
              # breaks = c(0.25, 0.5, 1, 2, 4)
              # fileName = NULL
              # summaryExclude = c("CCAE_UNM", "MDCR_UNM")

  
    seLogRr <- (logUb95Ci-logLb95Ci) / (2 * qnorm(0.975))
    
    include <- !(names %in% summaryExclude)
    
    meta <- meta::metagen(logRr[include], seLogRr[include], studlab = names[include], sm = "RR")
    s <- summary(meta)$random
    
    d1 <- data.frame(logRr = logRr,
                     logLb95Ci = logLb95Ci,
                     logUb95Ci = logUb95Ci,
                     name = labels,
                     type = "db")
    d2 <- data.frame(logRr = s$TE,
                     logLb95Ci = s$lower,
                     logUb95Ci = s$upper,
                     name = "Summary",
                     type = "ma")
    d3 <- data.frame(logRr = NA,
                     logLb95Ci = NA,
                     logUb95Ci = NA,
                     name = "Data source",
                     type = "header")
    d <- rbind(d1, d2, d3)
    
    idx <- which(is.na(d$logRr))
    d$logLb95Ci[idx] <- NA
    d$logUb95Ci[idx] <- NA

    d$name <- factor(d$name, 
                     levels = c("Summary", rev(as.character(labels)), "Source")
                     )

    p <- ggplot2::ggplot(d,ggplot2::aes(x = exp(logRr), 
                                        y = name, xmin = exp(logLb95Ci), xmax = exp(logUb95Ci))) +
        ggplot2::geom_vline(xintercept = breaks, colour = "#AAAAAA", lty = 1) +
        ggplot2::geom_vline(xintercept = 1, size = 0.5) +
        ggplot2::geom_errorbarh(height = 0.15, alpha = exp(0.5*(d$logLb95Ci-d$logUb95Ci))) +
        ggplot2::geom_point(size=3, shape = 23, ggplot2::aes(fill=type), alpha = exp(0.5*(d$logLb95Ci-d$logUb95Ci))) +
        ggplot2::scale_fill_manual(values = c("#000000", "#FFFFFF", "#FFFFFF")) +
        ggplot2::scale_x_continuous(xLabel, trans = "log10", breaks = breaks, labels = breaks) +
        ggplot2::coord_cartesian(xlim = c(min(breaks), max(breaks))) +
        ggplot2::theme(panel.grid.major = ggplot2::element_blank(),
              panel.grid.minor = ggplot2::element_blank(),
              panel.background = ggplot2::element_blank(),
              legend.position = "none",
              panel.border = ggplot2::element_blank(),
              axis.text.y = ggplot2::element_blank(),
              axis.title.y = ggplot2::element_blank(),
              axis.ticks = ggplot2::element_blank(),
              plot.margin = grid::unit(c(0,0,0.1,0), "lines"))
    
    rr <- exp(d$logRr)
    rrf <- formatC(rr,  digits = 2, format = "f")
    lo <- exp(d$logLb95Ci)
    lof <- formatC(lo,  digits = 2, format = "f")
    up <- exp(d$logUb95Ci)
    upf <- ifelse(up > 10, 
                  formatC(up,  digits = 1, format = "f"),
                  formatC(up,  digits = 2, format = "f"))
    

    labels <- ifelse(d$type == "header", paste(xLabel, "(95% CI)"), 
      ifelse(is.na(d$logRr), " -- ",
                     paste0(
                     rrf, # formatC(rr,  digits = 2, format = "f")
                     " (",
                     lof, # formatC(lo, digits = 2, format = "f"),
                     "-",
                     upf, # formatC(up, digits = digits, format = "f"),
                     ")")))

    labels <- data.frame(y = rep(d$name, 2),
                         x = rep(1:2, each = nrow(d)),
                         label = c(as.character(d$name), labels))
    
    # levels(labels$label)[1] <-  paste(xLabel,"(95% CI)")
    
    data_table <- ggplot2::ggplot(labels, 
                                  ggplot2::aes(x = x, y = y, label = label,
                                               parse = TRUE)) +
        ggplot2::geom_text(size = 4, hjust=0, vjust=0.5) +
        ggplot2::geom_hline(ggplot2::aes(yintercept=nrow(d) - 0.5)) +
        ggplot2::theme(panel.grid.major = ggplot2::element_blank(),
              panel.grid.minor = ggplot2::element_blank(),
              legend.position = "none",
              panel.border = ggplot2::element_blank(),
              panel.background = ggplot2::element_blank(),
              axis.text.x = ggplot2::element_text(colour="white"),#element_blank(),
              axis.text.y = ggplot2::element_blank(),
              axis.ticks = ggplot2::element_line(colour="white"),#element_blank(),
              plot.margin = grid::unit(c(0,0,0.1,0), "lines")) +
        ggplot2::labs(x="",y="") +
        ggplot2::coord_cartesian(xlim=c(1,3))

  #  plot <- gridExtra::grid.arrange(data_table, p, ncol=2)

    if (!is.null(fileName))
        ggplot2::ggsave(fileName, 
                        gridExtra::grid.arrange(data_table, p, ncol=2), 
                        width = 7, height = 1 + length(logRr) * 0.4, dpi = 400)

    return(list(data_table = data_table,
                p = p, 
                meta = meta))
}

  
  allCohorts <- read.csv(system.file("settings",
                                     "CohortsToCreate.csv",
                                     package = "AlendronateVsRaloxifene"))
  allCohorts <- allCohorts[3:nrow(allCohorts),]
  
buildOutcomeResults <- function(folders, analysisId, cohort, summaryExclude, allExclude = c()) {

  # analysisId <- 2
  # cohort <- "HipFracture"
  # allExclude <- c()
  
  allResults <- getData(folders)
  results <- allResults
  results <- results[results$analysisId == analysisId, ]
  results <- results[results$outcomeName == cohort, ]
  results <- results[results$db %in% folders, ]
  results$labels <- label3
  results <- results[!(results$db %in% allExclude),]
  
  results$logRr <- ifelse(abs(results$logRr) > 10, NA, results$logRr)
  
  results$order1 <- getOrder(results$db, folders)
  results <- results[order(results$order1,
                           decreasing = FALSE),]
  
  forest <- plotForest(logRr = results$logRr,
              logLb95Ci = log(results$ci95lb),
              logUb95Ci = log(results$ci95ub),
              names = results$db,
              labels = results$labels,
              xLabel = "Hazard Ratio",
              breaks = c(0.25, 0.5, 1, 2, 4),
              summaryExclude = summaryExclude,
              fileName = NULL)
}
  
 hip1 <- buildOutcomeResults(folders, analysisId = 1, cohort = "HipFracture",
                                c("CCAE_UNM", "MDCR_UNM"))
 gridExtra::grid.arrange(hip1$data_table, hip1$p, ncol = 2)
```

\clearpage

Meta-analysis:

```{r, echo=FALSE}
  hip1$meta
```

\clearpage
```{r, echo = FALSE, warning = FALSE}
ciCalibrationModelsIIT <- lapply(1:length(folders), FUN = function(idx) {
  file <- folders[idx]
  #print(file)
  emp <-  read.csv(file.path(studyFolder, 
                             file, "tablesAndFigures",
                             "EmpiricalCalibration.csv"))
  
  emp <- emp[emp$analysisId == 1 & emp$outcomeId %in% negControlCohortIds, ]
  model = EmpiricalCalibration::fitSystematicErrorModel(emp$logRr, emp$seLogRr, rep(0,nrow(emp)),
                                  estimateCovarianceMatrix = FALSE)
})

ciCalibrationModelsPP <- lapply(1:length(folders), FUN = function(idx) {
  file <- folders[idx]
  #print(file)
  emp <-  read.csv(file.path(studyFolder, 
                             file, "tablesAndFigures",
                             "EmpiricalCalibration.csv"))
  
  emp <- emp[emp$analysisId == 2 & emp$outcomeId %in% negControlCohortIds, ]
  model = EmpiricalCalibration::fitSystematicErrorModel(emp$logRr, emp$seLogRr, rep(0,nrow(emp)),
                                  estimateCovarianceMatrix = FALSE)
})

buildCalibratedOutcomeResults <- function(folders, analysisId, cohort, ciCalibrationModels, summaryExclude = c()) {
  allResults <- getData(folders)
  results <- allResults
  results <- results[results$analysisId == analysisId, ]
  results <- results[results$outcomeName == cohort, ]
  results <- results[results$db %in% folders, ]
  results$labels <- label3

  results$logRr <- ifelse(abs(results$logRr) > 10, NA, results$logRr)
  
  results$order1 <- getOrder(results$db, folders)
  results <- results[order(results$order1,
                           decreasing = FALSE),]
  
  #a = calibrateConfidenceInterval(logRr, seLogRr, model, ciWidth = 0.95)
  a = mapply(function(logRr, seLogRr, model, ciWidth) {
    return(EmpiricalCalibration::calibrateConfidenceInterval(logRr, seLogRr, model, ciWidth))
    }, results$logRr, results$seLogRr, ciCalibrationModels, rep(0.95, nrow(results)))
  
  results$newlogRr = unlist(a[c("logRr"),])
  results$newlogLb95Ci = unlist(a[c("logLb95Rr"),])
  results$newlogUb95Ci = unlist(a[c("logUb95Rr"),])
  
  forest <- plotForest(logRr = results$newlogRr,
              logLb95Ci = results$newlogLb95Ci,
              logUb95Ci = results$newlogUb95Ci,
              names = results$db,
              labels = results$labels,
              xLabel = "Hazard Ratio",
              breaks = c(0.25, 0.5, 1, 2, 4),
              summaryExclude = summaryExclude,
              fileName = NULL)
}
```

<!--
## Hip fracture CI Calibrated (intent-to-treat)
```{r, echo=FALSE, warning=FALSE}
 hip1CI <- buildCalibratedOutcomeResults(folders, analysisId = 1, cohort = "HipFracture",
                                ciCalibrationModelsIIT)
 gridExtra::grid.arrange(hip1CI$data_table, hip1CI$p, ncol = 2)
 #hip1CI$meta
```
-->

## Hip fracture effect estimate (per-protocol)
```{r, echo=FALSE, warning=FALSE}
hip2 <- buildOutcomeResults(folders, analysisId = 2, cohort = "HipFracture",
                                c("CCAE_UNM", "MDCR_UNM"),
                            c("PPlus","Cerner"))
 gridExtra::grid.arrange(hip2$data_table, hip2$p, ncol = 2)
```

\clearpage 

Meta-analysis:

```{r, echo=FALSE}
  hip2$meta
```
\clearpage

<!--
## Hip fracture CI Calibrated (per-protocol)
```{r, echo=FALSE, warning=FALSE}
hip2CI <- buildCalibratedOutcomeResults(folders, analysisId = 2, cohort = "HipFracture",
                                ciCalibrationModelsPP,
                            c("PPlus","Cerner"))
 gridExtra::grid.arrange(hip2CI$data_table, hip2CI$p, ncol = 2)
 #hip2CI$meta
```
-->

## Vertebral fracture effect estimate (intent-to-treat)
```{r, echo=FALSE, warning=FALSE}
vert1 <- buildOutcomeResults(folders, analysisId = 1, cohort = "VertebralFracture",
                                c("CCAE_UNM", "MDCR_UNM"))
 gridExtra::grid.arrange(vert1$data_table, vert1$p, ncol = 2)
```

\clearpage

Meta-analysis:

```{r, echo=FALSE}
  vert1$meta
```

\clearpage
<!--
## Vertebral fracture CI Calibrated (intent-to-treat)
```{r, echo=FALSE, warning=FALSE}
vert1CI <- buildCalibratedOutcomeResults(folders, analysisId = 1, cohort = "VertebralFracture",
                                ciCalibrationModelsIIT)
 gridExtra::grid.arrange(vert1CI$data_table, vert1CI$p, ncol = 2)
 #vert1CI$meta
```
-->

## Vertebral fracture effect estimate (per-protocol)
```{r, echo=FALSE, warning=FALSE}
vert2 <- buildOutcomeResults(folders, analysisId = 2, cohort = "VertebralFracture",
                                c("CCAE_UNM", "MDCR_UNM"),
                             c("PPlus","Cerner"))
 gridExtra::grid.arrange(vert2$data_table, vert2$p, ncol = 2)
```

\clearpage 

Meta-analysis:

```{r, echo=FALSE, warning=FALSE}
  vert2$meta
```

\clearpage
<!--
## Vertebral fracture CI Calibrated (per-protocol)
```{r, echo=FALSE, warning=FALSE}
vert2CI <- buildCalibratedOutcomeResults(folders, analysisId = 2, cohort = "VertebralFracture",
                                ciCalibrationModelsPP,
                            c("PPlus","Cerner"))
 gridExtra::grid.arrange(vert2CI$data_table, vert2CI$p, ncol = 2)
 #vert2CI$meta
```
-->

## Atypical femural fracture effect estimate (intent-to-treat)
```{r, echo=FALSE, warning=FALSE}
atyp1 <- buildOutcomeResults(folders, analysisId = 1, cohort = "AtypicalFemuralFracture",
                                c("CCAE_UNM", "MDCR_UNM"))
 gridExtra::grid.arrange(atyp1$data_table, atyp1$p, ncol = 2)
```

\clearpage

Meta-analysis:

```{r, echo=FALSE}
  atyp1$meta
```

\clearpage
<!--
## Atypical femural fracture CI Calibrated (intent-to-treat)
```{r, echo=FALSE, warning=FALSE}
atyp1CI <- buildCalibratedOutcomeResults(folders, analysisId = 1, cohort = "AtypicalFemuralFracture",
                                ciCalibrationModelsIIT)
 gridExtra::grid.arrange(atyp1CI$data_table, atyp1CI$p, ncol = 2)
 #atyp1CI$meta
```
-->

## Atypical femural fracture effect estimate (per-protocol)
```{r, echo=FALSE, warning=FALSE}
atyp2 <- buildOutcomeResults(folders, analysisId = 2, cohort = "AtypicalFemuralFracture",
                                c("CCAE_UNM", "MDCR_UNM"),
                             c("PPlus","Cerner"))
 gridExtra::grid.arrange(atyp2$data_table, atyp2$p, ncol = 2)
```

\clearpage

Meta-analysis:

```{r, echo=FALSE, warning=FALSE}
  atyp2$meta
```
\clearpage

<!--
## Atypical femural fracture CI Calibrated (per-protocol)
```{r, echo=FALSE, warning=FALSE}
atyp2CI <- buildCalibratedOutcomeResults(folders, analysisId = 2, cohort = "AtypicalFemuralFracture",
                                ciCalibrationModelsPP,
                            c("PPlus","Cerner"))
 gridExtra::grid.arrange(atyp2CI$data_table, atyp2CI$p, ncol = 2)
 #atyp2CI$meta
```
-->

## Esophageal Cancer effect estimate (intent-to-treat)
```{r, echo=FALSE, warning=FALSE}
ec1 <- buildOutcomeResults(folders, analysisId = 1, cohort = "EsophagealCancer",
                                c("CCAE_UNM", "MDCR_UNM"))
 gridExtra::grid.arrange(ec1$data_table, ec1$p, ncol = 2)
```

\clearpage

Meta-analysis:

```{r, echo=FALSE}
  ec1$meta
```

## Esophageal Cancer effect estimate (per-protocol)
```{r, echo=FALSE, warning=FALSE}
ec2 <- buildOutcomeResults(folders, analysisId = 2, cohort = "EsophagealCancer",
                                c("CCAE_UNM", "MDCR_UNM"),
                             c("PPlus","Cerner"))
 gridExtra::grid.arrange(ec2$data_table, ec2$p, ncol = 2)
```

\clearpage

Meta-analysis:

```{r, echo=FALSE}
  ec2$meta
```

## Osteonecrosis of the Jaw effect estimate (intent-to-treat)
```{r, echo=FALSE, warning=FALSE}
onj1 <- buildOutcomeResults(folders, analysisId = 1, cohort = "OsteonecrosisOfJaw",
                                c("CCAE_UNM", "MDCR_UNM"))
 gridExtra::grid.arrange(onj1$data_table, onj1$p, ncol = 2)
```

\clearpage

Meta-analysis:

```{r, echo=FALSE}
  onj1$meta
```

## Osteonecrosis of the Jaw effect estimate (per-protocol)
```{r, echo=FALSE, warning=FALSE}
onj2 <- buildOutcomeResults(folders, analysisId = 2, cohort = "OsteonecrosisOfJaw",
                                c("CCAE_UNM", "MDCR_UNM"),
                             c("PPlus","Cerner"))
 gridExtra::grid.arrange(onj2$data_table, onj2$p, ncol = 2)
```

\clearpage

Meta-analysis:

```{r, echo=FALSE}
  onj2$meta
```

\clearpage

```{r, echo = FALSE, warning = FALSE, fig.height=8, fig.width=7}
blank <- grid::grid.rect(gp=grid::gpar(col="white"))

cowplot::plot_grid(gridExtra::arrangeGrob(hip1$data_table, blank, hip1$p, ncol = 3, widths = c(1,0.1,1)),
                   gridExtra::arrangeGrob(blank),
                   gridExtra::arrangeGrob(vert1$data_table, blank, vert1$p, ncol = 3, widths = c(1,0.1,1)),
                   nrow = 3, labels=c('A) Hip Fracture',"",'B) Vert. Fracture'), label_fontface = "plain", 
                   vjust = 1, hjust = 0,
                   rel_heights = c(1,0.1,1))

cowplot::plot_grid(gridExtra::arrangeGrob(atyp1$data_table, blank, atyp1$p, ncol = 3, widths = c(1,0.1,1)),
                   gridExtra::arrangeGrob(blank),
                   gridExtra::arrangeGrob(ec1$data_table, blank, ec1$p, ncol = 3, widths = c(1,0.1,1)),
                   gridExtra::arrangeGrob(blank),
                   gridExtra::arrangeGrob(onj1$data_table, blank, onj1$p, ncol = 3, widths = c(1,0.1,1)),
                   nrow = 5, labels=c('A) AFF',"",'B) Eso. Cancer',"",'C) ONJ'), label_fontface = "plain",
                   vjust = 1, hjust = 0,
                   rel_heights = c(1,0.1,1,0.1,1))

# cowplot::plot_grid(gridExtra::arrangeGrob(hip1$data_table, hip1$p, blank, vert1$data_table, vert1$p,
#                                           ncol = 5, widths = c(1,1,.1,1,1)),
#                    gridExtra::arrangeGrob(atyp1$data_table, atyp1$p, blank, ec1$data_table, ec1$p,
#                                           ncol = 5, widths = c(1,1,.1,1,1)),
#                    gridExtra::arrangeGrob(onj1$data_table, onj1$p, blank, blank, blank,
#                                           ncol = 5, widths = c(1,1,.1,1,1)),
#                    nrow = 3)

```

## Top Covariate Balance
```{r, echo = FALSE, warning = FALSE}
.truncRight <- function(x, n) {
  nc <- nchar(x)
  x[nc > (n - 3)] <- paste("...",
                           substr(x[nc > (n - 3)], nc[nc > (n - 3)] - n + 1, nc[nc > (n - 3)]),
                           sep = "")
  x
}
plotCovariateBalanceOfTopVariables <- function(balance,
                                               n = 20,
                                               maxNameWidth = 100,
                                               fileName = NULL,
                                               beforeLabel = "before matching",
                                               afterLabel = "after matching") {
  topBefore <- balance[order(-abs(balance$beforeMatchingStdDiff)), ]
  topBefore <- topBefore[1:n, ]
  topBefore$facet <- paste("Top", n, beforeLabel)
  topAfter <- balance[order(-abs(balance$afterMatchingStdDiff)), ]
  topAfter <- topAfter[1:n, ]
  topAfter$facet <- paste("Top", n, afterLabel)
  filtered <- rbind(topBefore, topAfter)

  data <- data.frame(covariateId = rep(filtered$covariateId, 2),
                     covariate = rep(filtered$covariateName, 2),
                     difference = c(filtered$beforeMatchingStdDiff, filtered$afterMatchingStdDiff),
                     group = rep(c(beforeLabel, afterLabel), each = nrow(filtered)),
                     facet = rep(filtered$facet, 2),
                     rowId = rep(nrow(filtered):1, 2))
  filtered$covariateName <- .truncRight(as.character(filtered$covariateName), maxNameWidth)
  data$facet <- factor(data$facet, levels = rev(levels(data$facet)))
  data$group <- factor(data$group, levels = rev(levels(data$group)))
  plot <- ggplot2::ggplot(data, ggplot2::aes(x = difference,
                                             y = rowId,
                                             color = group,
                                             group = group,
                                             fill = group,
                                             shape = group)) +
    ggplot2::geom_point() +
    ggplot2::geom_vline(xintercept = 0) +
    ggplot2::scale_fill_manual(values = c(rgb(0.8, 0, 0, alpha = 0.5),
                                          rgb(0, 0, 0.8, alpha = 0.5))) +
    ggplot2::scale_color_manual(values = c(rgb(0.8, 0, 0, alpha = 0.5),
                                           rgb(0, 0, 0.8, alpha = 0.5))) +
    ggplot2::scale_x_continuous("Standardized difference of mean") +
    ggplot2::scale_y_continuous(breaks = nrow(filtered):1, labels = filtered$covariateName) +
    ggplot2::facet_grid(facet ~ ., scales = "free", space = "free") +
    ggplot2::theme(axis.text.y = ggplot2::element_text(size = 7),
                   axis.title.y = ggplot2::element_blank(),
                   legend.position = "top",
                   legend.direction = "horizontal",
                   legend.title = ggplot2::element_blank())
  if (!is.null(fileName))
    ggplot2::ggsave(fileName, plot, width = 10, height = max(2 + n * 0.2, 5), dpi = 400)
  return(plot)
}

plotCovariateBalanceOfTopVariables1 <- function(balance,
                                               n = 20,
                                               maxNameWidth = 100,
                                               fileName = NULL,
                                               beforeLabel = "before matching",
                                               afterLabel = "after matching") {
  topBefore <- balance[order(-abs(balance$beforeMatchingStdDiff)), ]
  topBefore <- topBefore[1:n, ]
  topBefore$facet <- paste("Top", n, beforeLabel)
  # topAfter <- balance[order(-abs(balance$afterMatchingStdDiff)), ]
  # topAfter <- topAfter[1:n, ]
  # topAfter$facet <- paste("Top", n, afterLabel)
  # filtered <- rbind(topBefore, topAfter)
  filtered <- topBefore

  data <- data.frame(covariateId = rep(filtered$covariateId, 2),
                     covariate = rep(filtered$covariateName, 2),
                     difference = c(filtered$beforeMatchingStdDiff, filtered$afterMatchingStdDiff),
                     group = rep(c(beforeLabel, afterLabel), each = nrow(filtered)),
                     #facet = rep(filtered$facet, 2),
                     rowId = rep(nrow(filtered):1, 2))
  filtered$covariateName <- .truncRight(as.character(filtered$covariateName), maxNameWidth)
  #data$facet <- factor(data$facet, levels = rev(levels(data$facet)))
  data$group <- factor(data$group, levels = rev(levels(data$group)))
  plot <- ggplot2::ggplot(data, ggplot2::aes(x = difference,
                                             y = rowId,
                                             color = group,
                                             group = group,
                                             fill = group,
                                             shape = group)) +
    ggplot2::geom_point() +
    ggplot2::geom_vline(xintercept = 0) +
    ggplot2::scale_fill_manual(values = c(rgb(0.8, 0, 0, alpha = 0.5),
                                          rgb(0, 0, 0.8, alpha = 0.5))) +
    ggplot2::scale_color_manual(values = c(rgb(0.8, 0, 0, alpha = 0.5),
                                           rgb(0, 0, 0.8, alpha = 0.5))) +
    ggplot2::scale_x_continuous("Standardized difference of mean") +
    ggplot2::scale_y_continuous(breaks = nrow(filtered):1, labels = filtered$covariateName) +
    #ggplot2::facet_grid(facet ~ ., scales = "free", space = "free") +
    ggplot2::theme(axis.text.y = ggplot2::element_text(size = 7),
                   axis.title.y = ggplot2::element_blank(),
                   legend.position = "top",
                   legend.direction = "horizontal",
                   legend.title = ggplot2::element_blank())
  if (!is.null(fileName))
    ggplot2::ggsave(fileName, plot, width = 10, height = max(2 + n * 0.2, 5), dpi = 400)
  return(plot)
}


balance = read.csv("~/Dropbox/Hip_Fracture_Paper/prettyBalance/Balance.csv")
plotCovariateBalanceOfTopVariables1(balance,
                                    n = 20,
                                    maxNameWidth = 100,
                                    fileName = "~/Dropbox/Hip_Fracture_Paper/prettyBalance/balance.png",
                                    beforeLabel = "before matching",
                                    afterLabel = "after matching")
```

## Negative Control Figure
```{r, echo = FALSE, warning = FALSE}
# select Optum
idx = 2
file <- folders[idx]
emp <-  read.csv(file.path(studyFolder, 
                           file, "tablesAndFigures",
                           "EmpiricalCalibration.csv"))

emp <- emp[emp$analysisId == 1 & emp$outcomeId %in% negControlCohortIds, ]
plot1 <- EmpiricalCalibration::plotCalibrationEffect(emp$logRr, emp$seLogRr)
plot2 <- EmpiricalCalibration::plotCalibration(emp$logRr, emp$seLogRr, legendPosition = c(0.675,0.20))
#blank <- grid::grid.rect(gp=grid::gpar(col="white"))
# ggplot2::ggsave("banana.png",
#                 gridExtra::grid.arrange(cowplot::plot_grid(plot1,  plot2,
#                                            nrow = 1, labels = c('A)','B)'),
#                                            label_fontface = "plain", vjust = 1.05, hjust = 0,
#                                            rel_widths = c(1,1))),
#                 dpi = 600, width = 6, height = 3, units = "in")
gridExtra::grid.arrange(cowplot::plot_grid(plot1,  plot2,
                                           nrow = 1, labels = c('A)','B)'),
                                           label_fontface = "plain", vjust = 1.05, hjust = 0,
                                           rel_widths = c(1,1)))
```






